\documentclass[11pt]{article}

\usepackage{url}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{times}
\usepackage{graphicx}


\begin{document}

\title{Data Center Marketing System}
\author{Rui Zhou \and Shu Zhang}
\date{Final Project - CSCI 2950-u - Spring 2013}
\maketitle

\begin{abstract}
In this report we present the auction-based marketing system we build for data center applications.
Motivited by similar mechanism of auctions for resource in other computer systems, we aim to 
let users bid their network resouces, mainly bandwidth and latency of their desired flows. Different from existing 
bidding systems like Google's marketing system\cite{google}, our system is based on SDN network and utilizes the advantage
of the central controller and global network information. 
Another thing we focus on is the allocation algorithm for the auctioneer. We investigated some 
algorithms and evaluated their performances. 
\end{abstract}

\section{Introduction}

\section{Related Work}
\subsection{Data Center Markets}
\subsection{Existing Pricing Mechanisms}
\subsection{Software Defined Network}
\subsubsection{OpenFlow}
\subsubsection{Floodlight}
\section{System Design and Algorithm}

\section{Implementation}

\section{Evaluation}

\section{Conclusions}

It should be easy to write your report in LaTeX, and it's a great tool
to learn. It almost certainly came with your Linux installation, and
can be very easily installed in Cygwin and on the Mac (through the
excellent MacTeX distribution).

\bibliographystyle{plain}
\begin{thebibliography}{99}
 \bibitem{aws} Amazon Web Services: http://aws.amazon.com.
 \bibitem{ec2} Amazon EC2 Pricing: http://aws.amazon.com/ec2/pricing.
 \bibitem{spot} EC2 Spot Instances: http://aws.amazon.com/ec2/spot-instances.
 \bibitem{google} Stokely, Murray, et al. "Using a market economy to provision compute resources across planet-wide clusters." Parallel \& Distributed Processing, 2009. IPDPS 2009. IEEE International Symposium on. IEEE, 2009.
 \bibitem{combinatorial auction} Nisan, Noam. "Bidding and allocation in combinatorial auctions." Proceedings of the 2nd ACM conference on Electronic commerce. ACM, 2000.
 \bibitem{ucsd} AuYoung, Alvin, et al. Practical market-based resource allocation. University of California, San Diego, 2010.
 \bibitem{dartmouth} Bredin, Jonathan, David Kotz, and Daniela Rus. "Market-based resource control for mobile agents." Proceedings of the second international conference on Autonomous agents. ACM, 1998.
 \bibitem{second price} Vickrey, William. "Counterspeculation, auctions, and competitive sealed tenders." The Journal of finance 16.1 (1961): 8-37.
 \bibitem{clock1} Ausubel, Lawrence M., and Peter Cramton. "Auctioning many divisible goods." Journal of the European Economic Association 2.23 (2004): 480-493.
 \bibitem{clock2} Cramton, Peter, and Lawrence M. Ausubel. "The clock-proxy auction: A practical combinatorial auction design." (2006): 115-138.
\end{thebibliography}

\end{document}
